### 2020-07-12 paper.tex
Add text on Radon-Nikodym to the differentiable language section

\section{INVOLUTIVE MCMC} \label{sec:involutive-mcmc}
Let $(X, \Sigma_P, \mu_P)$ and $(Y, \Sigma_Q, \mu_Q)$ denote two measure spaces with $\sigma$-finite $\mu_P$ and $\mu_Q$.
Let $p : X \to [0, \infty)$ be a probability density with respect to $\mu_P$ and for each $x \in X$ such that $p(x) > 0$ let $q_x : Y \to [0, \infty)$ be probability density with respect to $\mu_Q$.
We call $p$ the \emph{model density} and we call $q_x$ \emph{auxiliary densities}.
Let $\pi(x, y) := p(x) q_x(y)$ and $Z := \{(x, y) \in X \times Y : \pi(x, y) > 0 \}$.
Suppose that $Z \in \Sigma_P \otimes \Sigma_Q$ ($Z$ is a $\mu_P \times \mu_Q$-measurable set).
Then $\Sigma := \{A \in \Sigma_P \otimes \Sigma_Q : A \subseteq Z\}$ is a $\sigma$-algebra on $Z$ and $\mu : \Sigma \to [0, \infty)$ with $\mu(A) := (\mu_P \times \mu_Q)(A)$ is a $\sigma$-finite measure on measurable space $(Z, \Sigma)$.

@@

@@

>>>>

\section{INVOLUTIVE MCMC} \label{sec:involutive-mcmc}
This section gives a measure-theoretic formulation of involutive MCMC on general state spaces.
This generality is necessary for applications of involutive MCMC to models with structure uncertainty and for describing how involutive MCMC can be automated using probabilistic programming.

Let $(X, \Sigma_P, \mu_P)$ and $(Y, \Sigma_Q, \mu_Q)$ denote two measure spaces with $\sigma$-finite $\mu_P$ and $\mu_Q$.
Let $p : X \to [0, \infty)$ be a probability density with respect to $\mu_P$ and for each $x \in X$ such that $p(x) > 0$ let $q_x : Y \to [0, \infty)$ be probability density with respect to $\mu_Q$.
We call $p$ the \emph{model density} and we call $q_x$ \emph{auxiliary densities}.
Let $\pi(x, y) := p(x) q_x(y)$ and $Z := \{(x, y) \in X \times Y : \pi(x, y) > 0 \}$.
Suppose that $Z \in \Sigma_P \otimes \Sigma_Q$ ($Z$ is a $\mu_P \times \mu_Q$-measurable set).
Then $\Sigma := \{A \in \Sigma_P \otimes \Sigma_Q : A \subseteq Z\}$ is a $\sigma$-algebra on $Z$ and $\mu : \Sigma \to [0, \infty)$ with $\mu(A) := (\mu_P \times \mu_Q)(A)$ is a $\sigma$-finite measure on measurable space $(Z, \Sigma)$.

@@

TODO: show an example

@@

\subsection{The Radon-Nikodym Derivative}

The differentiable programming language introduced in this section assumes that the reference measure of each random choice address is either the counting measure (corresponding to the $\mathtt{:}\mathtt{discrete}$ tag in \texttt{@read} and \texttt{@write} operations) or a Lebesgue measure ($\mathtt{:}\mathtt{continuous}$ tag).
Consider a bijection $f : Z \to Z$ (recall that every involution is a bijection).
If the space $Z$ can be partitioned into a countable number of sets $Z_1, Z_2, \ldots$, such that the each element of the partition is in one-to-one correspondence with another element ($f_1 : \{Z_1, Z_2, \ldots\} \to \{Z_1, Z_2, \ldots\}$ for some bijection $f_1$), and such that $f_{2,i} : Z_i \to Z_{f_1(i)}$ is a continuously differentiable bijection, and such that $f(z) = f_{2,i(z)}(z)$, then a Radon-Nikodym can be constructed from the Jacobian of the function $f_{2,i(z)}$ where $i(z) = Z_j$ for $z \in Z_j$.
See Section~\ref{sec:radon-nikodym-special-case} of the appendix for details.
Applying this to the setting where $Z$ is a set of pairs of traces of probabilistic programs as formalized in the preivous section is straightforward when the partition of $Z$ is the countable disjoint union over all pairs $(A, \mathbf{d})$ where $A \subseteq \mathcal{A}$ are trace structures and $\mathbf{d}$ are assignments to discrete choices.
